---
title: "Homework 10"
output: 
  html_document:
    highlight: tango
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggthemes)
library(knitr)
library(gt)

theme_set(theme_minimal())

```

#### 1. Create a new RStudio Project and modify the YAML to: 

* Render to html
* Change the syntax highlighting to any scheme but the default 
* Include code folding


#### 2a. Reorder **factors**

* Get familiar with the `gss_cat` data within the `{forcats}` package.
* Remove the rows with missing data in the *tvhours* column.
* Calculate the mean *tvhours* by *marital status*.
* Display the results as a point plot of average TV consumption by marital status (*tvhours* on the *x*-axis and *martial* on they *y*-axis).
  + In your plot, `reorder` the levels of *marital* according to *tvhours*.
* Give your plot meaningful axis labels and a title.

```{r factors, include=FALSE}

marital_means <- gss_cat %>%
  #filter(!is.na(tvhours))
  drop_na(tvhours) %>%
  group_by(marital) %>%
  summarise(tvhours_mean = mean(tvhours, na.rm = TRUE))

marital_means %>% 
  ggplot(aes(tvhours_mean, fct_reorder(marital, tvhours_mean))) +
  geom_point() +
  labs(y = "Marital Status",
       x = "TV Hours/Day",
       title = "Mean TV Hours/Day by Marital Status")

```

#### 2b. Working with **tables**

* Display the same results (mean *tvhours* by *marital status*) as a table using `kable()`.
  + Change the column names.
  + Round the mean *tvhours* to one decimal.
  + Bold the row with the highest mean *tvhours*.
  
```{r}
marital_means %>% 
  arrange(desc(tvhours_mean)) %>% 
  knitr::kable(
    col.names = c("Marital Status", "Mean TV Hours/Day"),
    digits = 1
  ) %>% 
  kableExtra::row_spec(1, bold = TRUE)

```
  

#### 3a. Recode **factors**

* Use any of the functions we talked about in class to display the levels of the *marital* variable.
* `recode` or `collapse` the *marital* column into three categories: "Not married", "Married", and "No answer".
* Calculate the mean *tvhours* by *marital status*.
* Display the results as a column plot of average TV consumption by marital status (*martial* on the *x*-axis and *tvhours* on they *y*-axis).
  + From left to right, the columns in your plot should read: "Not married", "Married", and "No answer".
* Make your plot look a little nicer with some color, different theme, meaningful axis labels, and a title.
  

```{r, include=FALSE}

levels(gss_cat$marital)
table(gss_cat$marital)

gss_cat %>% 
  count(marital)

gss_cat %>% 
  mutate(marital = fct_collapse(marital,
                                "Not married" = c("Never married", "Separated", "Divorced", "Widowed"),
                                "Married" = c("Married"),
                                "No answer" = c("No answer"))) %>% 
  group_by(marital) %>% 
  summarise(tvhours_mean = mean(tvhours, na.rm = TRUE)) %>%
  ggplot(aes(fct_relevel(marital, "Not married", "Married"), tvhours_mean)) +
  geom_col(aes(fill = marital)) +
  scale_fill_colorblind() +
  labs(y = "Marital Status",
       x = "TV Hours/Day",
       title = "Mean TV Hours/Day by Marital Status") +
  theme(legend.position = "none")

```

#### 3b. Working with **tables**

* Display the same results (mean *tvhours* by collapsed *marital status*) as a table using the `{gt}`.
  + Change the column names.
  + Round the mean *tvhours* to one decimal.
  + Highlight in yellow the row with the lowest mean *tvhours*.
  
```{r}
gss_cat %>% 
  mutate(marital = fct_collapse(marital,
                                "Not married" = c("Never married", "Separated", "Divorced", "Widowed"),
                                "Married" = c("Married"),
                                "No answer" = c("No answer"))) %>% 
  group_by(marital) %>% 
  summarise(tvhours_mean = mean(tvhours, na.rm = TRUE)) %>% 
  arrange(tvhours_mean) %>% 
  gt() %>% 
  fmt_number(
    columns = 2,
    decimals = 1
  ) %>% 
  tab_style(
    style = cell_fill(color = "yellow"),
    locations = cells_body(
      columns = c(1, 2),
      rows = 3
    )
  ) %>% 
  cols_label(
    marital = "Marital Status",
    tvhours_mean = "Mean TV hours/day"
  )

```
  

This lab borrows from [Garrett Grolemund's](https://resources.rstudio.com/authors/garrett-grolemund) [Remaster the Tidyverse](https://github.com/rstudio-education/remaster-the-tidyverse/) materials. 
